### 2012-03-29 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: In progress.

Each occurrence of a join pattern is classified by application of the following rules it this specific order. The first satisfied ruled is applied. The occurrence is also assigned with a weight determining how sure the method is about the inferred statement.

The pattern occurrence is considered of case (O1) if it is the for join pattern (weight: 1), if aggregation function \texttt{avg}, \texttt{min}, \texttt{max} or \texttt{sum} is applied on a target return path (weight: 1) or if aggregation function \texttt{count} is applied on a target return path (weight: 0.75), where target return paths are paths in $C_R$ starting with $\$e_2$ (see Listing \ref{listing_for_join_pattern}).

Otherwise, the pattern occurrence is considered of case (O2) and the assigned weight depends on the number of target return paths. If the number is greater than one, the weight is one (weight: 1), else (the number equals zero or one) the weight is one half (weight: 0.5).

>>>>

Each occurrence of a join pattern is classified by application of the following rules R1 - R5 in this specific order. The first satisfied rule is applied. The occurrence is also assigned with a weight determining how sure the method is about the inferred statement.

The pattern occurrence is considered of case (O1) if it is the for join pattern (R1, weight: 1), if aggregation function \texttt{avg}, \texttt{min}, \texttt{max} or \texttt{sum} is applied on a target return path (R2, weight: 1) or if aggregation function \texttt{count} is applied on a target return path (R3, weight: 0.75), where target return paths are paths in $C_R$ starting with $\$e_2$ (see Listing \ref{listing_for_join_pattern}).

Otherwise, the pattern occurrence is considered of case (O2) and the assigned weight depends on the number of target return paths. If the number is greater than one, the weight is one (R4, weight: 1), else (the number equals zero or one) the weight is one half (R5, weight: 0.5).

### 2012-03-29 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\subsection{Expression Types}
\begin{itemize}
\item XML Schema built-in atomic types. See Attachment \ref{FIG_xsd_built_in_atomic_types}. \todo{Kludne do textu}
\item Types \emph{ElementType}, \emph{AttributeType}, \emph{NodeType}, \emph{TextNodeType},\linebreak \emph{CommentType}, \emph{ProcessingInstructionType}, \emph{DocumentType} representing an element, attribute, node, text node, comment, processing instruction, document node.
\item Type representing a node or a set of nodes selected by a certain path expression. The path expression is included in this type. Let this type be identified as \emph{PathType}.
\item \emph{UnknownType} representing a type without known details, which does not suit one of the three previous types. An example is XSD type \texttt{anyType}.
\end{itemize}

@@

\subsection{Definition of Keys}
To define a key and a foreign key, we adopt the definitions introduced in the original approach \cite{Necasky:2009:DXK:1529282.1529414} with a modification that XPath paths are replaced by PathType instances.

\begin{define}[Key]
A key is a construct $(C, P, \{L\})$, where $C$, $P$ and $L$ are PathType instances without predicates and without special function calls that use only child and descendant axes. $C$ is called \emph{context path}, $P$ \emph{target path} and $L$ \emph{key path}. $C$ can be omitted, i.e. we can write $(P, \{L\})$. This is equivalent to $(/, P, \{L\})$. If $C$ is omitted we call the key \emph{global key}. Otherwise, it is called \emph{relative key}.
\end{define}

\begin{define}[Foreign key]
A foreign key is a construct $(C, (P_1, \{L_1\}) \rightarrow (P_2, \{L_2\}))$, where $(C, P_2, \{L_2\})$ is a key and $P_1$ and $L_1$ are PathType instances without predicates and without special function calls that use only child and descendant axes. $C$ can be omitted as in the case of keys.
\end{define}

\todo[inline]{priklad}

@@

As described in the original method and summarized in Chapter \ref{Keys} we recognize two cases (O1) and (O2) of inference of keys from occurrences of the join patterns, and rules (R1 - R5) \todo{V sekci 3.5 zadna takova nevidim} to classify each occurrence into one of these cases. For the join pattern 3, we introduce a new rule, considering the join pattern 3 of case (O1), assigned with weight of 0.5.  The lesser weight is chosen because there is a lower probability that join of the join pattern 3 type is done via a key/foreign key pair.

@@

\todo[inline]{Zlucovanie vah s klucmi.}

@@

@@

Let $K_1, \dots, K_n$ be the inferred keys. Let $S_i$ be the score of $K_i$ and $N_i$ be the number of the inferred statements about $K_i$. Let $S^{max}$ be the maximum from $|S_1|, \dots , |S_n|$ and $N^{max}$ be the maximum norm
from $N_1, \dots , N_n$. The normalized score $S_i$ of $K_i$ is computed as $S^{norm}_i = \frac{S_i}{S^{max}} * (1 - \frac{N^{max} - N_i}{\sum_{i=1}^{n}N_i})$

>>>>

\subsection{Expression Types}
\begin{figure}
\caption{XSD built-in atomic types.}
\label{FIG_xsd_built_in_atomic_types}
\includegraphics[scale=0.65]{xsd-types.eps}
\end{figure}

\begin{itemize}
\item XML Schema built-in atomic types. See Figure \ref{FIG_xsd_built_in_atomic_types}.
\item Types \emph{ElementType}, \emph{AttributeType}, \emph{NodeType}, \emph{TextNodeType},\linebreak \emph{CommentType}, \emph{ProcessingInstructionType}, \emph{DocumentType} representing an element, attribute, node, text node, comment, processing instruction, document node.
\item Type representing a node or a set of nodes selected by a certain path expression. The path expression is included in this type. Let this type be identified as \emph{PathType}.
\item \emph{UnknownType} representing a type without known details, which does not suit one of the three previous types. An example is XSD type \texttt{anyType}.
\end{itemize}

@@

\subsection{Definition of Keys}
To define a key and a foreign key, we adopt the definitions introduced in the original approach \cite{Necasky:2009:DXK:1529282.1529414} with the following modifications.

\begin{itemize}
\item XPath paths are replaced by PathType instances.
\item All paths can use also descendant or self axis.
\item \emph{Key paths} can use also attribute axis.
\end{itemize}

The modified definitions are as follows.

\begin{define}[Key]
A key is a construct $(C, P, \{L\})$, where $C$, $P$ and $L$ are PathType instances without predicates and without special function calls that use only child, descendant, and descendant or self ($L$ also attribute) axes. $C$ is called \emph{context path}, $P$ \emph{target path} and $L$ \emph{key path}. $C$ can be omitted, i.e. we can write $(P, \{L\})$. This is equivalent to $(/, P, \{L\})$. If $C$ is omitted we call the key \emph{global key}. Otherwise, it is called \emph{relative key}.
\end{define}

\begin{define}[Foreign key]
A foreign key is a construct $(C, (P_1, \{L_1\}) \rightarrow (P_2, \{L_2\}))$, where $(C, P_2, \{L_2\})$ is a key and $P_1$ and $L_1$ are PathType instances without predicates and without special function calls that use only child, descendant, and descendant or self ($L$ also attribute) axes. $C$ can be omitted as in the case of keys.
\end{define}

An example of a global key is \texttt{(/site/people/person, \{@id\})}. An example of a foreign key to that key is  \texttt{((/site/closed\_auctions/closed\_auction, \{buyer/@person\}) $\rightarrow$ (/site/people/person, \{@id\}))}.

@@

As described in the original method and summarized in Chapter \ref{Keys} we recognize two cases (O1) and (O2) of inference of keys from occurrences of the join patterns, and rules (R1 - R5) to classify each occurrence into one of these cases. For the join pattern 3, we introduce a new rule, considering the join pattern 3 of case (O1), assigned with weight of 0.5.  The lesser weight is chosen because there is a lower probability that join of the join pattern 3 type is done via a key/foreign key pair.

@@

@@

\todo[inline]{Definicia NUS a context Path, podobne ako v klucoch.}

@@

Let $K_1, \dots, K_n$ be the inferred keys. Let $S_i$ be the score (the sum of weights) of $K_i$  and $N_i$ be the number of the inferred statements about $K_i$.

Let $NU_1, \dots, NU_m$ be the discovered negative uniqueness statements. Let $W_j$ be the weight of $NU_j$.

The negative uniqueness statements affect the scores as follows. For each negative uniqueness statement $NU_j = (C^{NU}_j, P^{NU}_j)$, find $\mathcal{K}_j$ set of keys which are rejected by the statement. 
\begin{center}
$\mathcal{K}_j = \Bigl \{K_i = (C^K_i, P^K_i, \{L^K_i\}) \Big | C^{NU}_j = C^K_i, P^{NU}_j = P^K_i/L^K_i\Bigr \}$.
\end{center}
Then, for each key $K_i \in \mathcal{K}_j$ decrement its score $S_i$ with weight of the negative uniqueness statement $W_j$.

Let $S^{max}$ be the maximum from $|S_1|, \dots , |S_n|$ and $N^{max}$ be the maximum norm
from $N_1, \dots , N_n$. The normalized score $S_i$ of $K_i$ is computed as
\begin{center}
$S^{norm}_i = \frac{S_i}{S^{max}} * (1 - \frac{N^{max} - N_i}{\sum_{i=1}^{n}N_i})$
\end{center}
